Reference label transfer of the fetal kidney reference (Stewart et al.) for `r params$sample_id`

### 2024-08-19 analyses/cell-type-wilms-tumor-06/notebook_template/02a_label-transfer_fetal_full_reference_Cao.Rmd
Changes to PR#706

```{r run_azimuth, message=FALSE, warnings=FALSE}
DefaultAssay(srat) <- "RNA"
s <- RunAzimuth(srat, reference ="fetusref" )

# We transfer the annotation to the pre-processed `Seurat`iobject as we don't want to keep changes done on the query by `RunAzimuth`
metadata_to_trasfer <- s@meta.data[, c("predicted.annotation.l1.score", "predicted.annotation.l1", "predicted.annotation.l2.score", "predicted.annotation.l2", "predicted.organ.score", "predicted.organ")]
srat <- AddMetaData(srat, metadata_to_trasfer, col.name = c("fetal_full_predicted.annotation.l1.score", "fetal_full_predicted.annotation.l1", "fetal_full_predicted.annotation.l2.score", "fetal_full_predicted.annotation.l2", "fetal_full_predicted.organ.score", "fetal_full_predicted.organ"))
```

@@

f1 <- SCpubr::do_BarPlot(sample = srat,
                         group.by = "fetal_full_predicted.organ",
                         split.by = "seurat_clusters",
                         position = "fill",
                         font.size = 10,
                         legend.ncol = 4) +
                         ggtitle("% cells")+
                         xlab(file)

>>>>

```{r run_azimuth, message=FALSE, warnings=FALSE}
DefaultAssay(srat) <- "RNA"
options(future.globals.maxSize= 8912896000000)
s <- RunAzimuth(srat, reference ="fetusref" )

# We transfer the annotation to the pre-processed `Seurat`iobject as we don't want to keep changes done on the query by `RunAzimuth`
metadata_vec <- c("predicted.annotation.l1.score", "predicted.annotation.l1", "predicted.annotation.l2.score", "predicted.annotation.l2", "predicted.organ.score", "predicted.organ")

metadata_to_trasfer <- s@meta.data[, metadata_vec]

srat <- AddMetaData(srat, metadata_to_trasfer, col.name = paste0("fetal_full_", metadata_vec))
```

@@

f1 <- SCpubr::do_BarPlot(sample = srat,
                         group.by = "fetal_full_predicted.organ",
                         split.by = "seurat_clusters",
                         position = "fill",
                         font.size = 10,
                         legend.ncol = 4) +
                         ggtitle("% cells")+
                         xlab(params$sample_id)

### 2024-08-19 analyses/cell-type-wilms-tumor-06/notebook_template/02b_label-transfer_fetal_kidney_reference_Stewart.Rmd
Changes to PR#706

```{r run_azimuth, message=FALSE, warnings=FALSE}

data <-  RunAzimuth(srat, path_to_reference, assay = 'RNA')
# We transfer the annotation to the pre-processed `Seurat`object as we don't want to keep changes done on the query by `RunAzimuth`
metadata_to_trasfer <- data@meta.data[, c("predicted.compartment.score", "predicted.compartment", "predicted.cell_type.score", "predicted.cell_type")]
srat <- AddMetaData(srat, metadata_to_trasfer, col.name = c("fetal_kidney_predicted.compartment.score", "fetal_kidney_predicted.compartment", "fetal_kidney_predicted.cell_type.score", "fetal_kidney_predicted.cell_type"))
```

>>>>

```{r run_azimuth, message=FALSE, warnings=FALSE}
DefaultAssay(srat) <- "RNA"
options(future.globals.maxSize= 8912896000000)

data <-  RunAzimuth(srat, path_to_reference, assay = 'RNA')
# We transfer the annotation to the pre-processed `Seurat`object as we don't want to keep changes done on the query by `RunAzimuth`
# We transfer the annotation to the pre-processed `Seurat`iobject as we don't want to keep changes done on the query by `RunAzimuth`
metadata_vec <- c("predicted.compartment.score", "predicted.compartment", "predicted.cell_type.score", "predicted.cell_type")
metadata_to_trasfer <- s@meta.data[, metadata_vec]
srat <- AddMetaData(srat, metadata_to_trasfer, col.name = paste0("fetal_full_", metadata_vec))

```
